Holomorphic field theories and higher algebra

### 2024-09-19 draft.tex
first full pass thru holo FT section

\subsubsection{Holomorphic gauge theories}

@@

Note that for the notion introduced in Section~\ref{sec: pert dfn},
it is straightforward to provide such a homotopical trivialization: 
the fields are encoded by a Dolbeault complex on $\CC^n$, 
translations act by the Lie derivative $L_{\partial/\partial x_j}$,
and so we trivialize the action $L_{\partial/\partial \zbar_j}$ by using the contraction $\iota_{\partial/\partial \zbar_j}$,
thanks to Cartan's formula.

We now turn to using this point of view in the setting of supersymmetric theories

@@

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
We focus on Euclidean field theories and work in Riemannian signature,
hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
$\mathfrak{so}(d) \ltimes \ft$
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\beqn
\label{e:Gamma}
\Gamma \colon {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\eeqn
by the formula $[\cQ, \cQ'] = \Gamma(\cQ, \cQ')$.

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of twisting supercharges is a completely algebraic question,
and we refer to~\autocite{ESsusy} for a complete classification for supersymmetry algebras in dimensions from $1$ to~$10$.

If a Lagrangian field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^\cQ$ of $\cT^\cQ$ has the form
\[
S^\cQ(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(\cQ \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $\cQ$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $\cQ$).
For extensive details on how the twisted theory is defined we refer to~\autocite{CostelloHolomorphic, ESW}.

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories.
In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist rendering the theory holomorphic.\footnote{This fails in one example where the dimension and amount of supersymmetry is too small, namely for $\cN=(1,0)$ supersymmetry in two dimensions.}
Indeed, so long as a twisted supercharge is nonzero $\cQ \ne 0$ one see that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly $n$, 
and we declare the the image of $\cQ$ is spanned by the anti-holomorphic vector fields $\{\del / \del \zbar_i\}$.
Thus there exist homotopies $\{\eta_i\}$ such that 
\beqn
[\cQ,\eta_i] = \frac{\del}{\del \zbar_i} ,
\eeqn 
recovering the characterization of holomorphic field theories mentioned at the beginning of the subsection.

%For our purposes here, a crucial property of a twist $Q$ is the dimension $k_Q$ of its image ${\rm Im} \; \Gamma(Q, \cdot) \subset \RR^d$,
%which we call the number of {\em invariant} directions of~$Q$.
%By the non-degeneracy of the pairing $\Gamma$, it follows that $k_Q \geq \frac{d}{2}$.
%If the number of invariant directions is maximal with $k_Q = d$, then the twisted theory $\cT^Q$ is purely topological. 
%If the number of invariant directions is minimal with $k_Q = \frac{d}{2}$, then the twisted theory $\cT^Q$ is purely holomorphic.

As a representative example of how twisting behaves, 
consider pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry.
The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional and there exists a unique holomorphic twist $\cQ$ (up to equivalence).
In this dimension, with this amount of supersymmetry, there does not exist a topological twist.
The holomorphic twist of the theory with respect to $\cQ$ is equivalent to holomorphic BF theory on $\CC^2$.

This ends our discussion of twisting supersymmetric gauge theories.
There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list.

\begin{itemize}
\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
For instance, the closed string field theory of the topological B-model on a Calabi--Yau threefold is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
This theory is defined on any Calabi--Yau manifold. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory in other dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory you start with on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, holomorphic BF theory on (super) twistor space associated to $\RR^4$ is equivalent to a self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}

@@

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!

>>>>

\subsubsection{Holomorphic gauge theories}
\label{sec: hol BF dfn}

@@

Note that for the notion introduced in Section~\ref{sec: pert dfn},
it is straightforward to provide such a homotopical trivialization: 
the fields are encoded by a Dolbeault complex on $\CC^n$, 
a real translation $\partial/\partial x_j$ acts by the Lie derivative $L_{\partial/\partial x_j}$,
and so we trivialize the action $L_{\partial/\partial \zbar_j}$ by using the contraction $\iota_{\partial/\partial \zbar_j}$,
thanks to Cartan's formula.

We now turn to using this point of view in the setting of supersymmetric theories.

@@

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
We focus on Euclidean field theories and work in Riemannian signature,
so for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
$\mathfrak{so}(d) \ltimes \ft$
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\beqn
\label{e:Gamma}
\Gamma \colon {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\eeqn
by the formula $[\cQ, \cQ'] = \Gamma(\cQ, \cQ')$.

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of twisting supercharges is a completely algebraic question:
see~\autocite{ESsusy} for a complete classification in dimensions from $1$ to~$10$.

In even dimensions $d = 2n$, basic properties of the supersymmetry algebra guarantee that there exists a twist that provides a complex structure to $\RR^{2n}$.\footnote{This claim fails in exactly one example, namely for $\cN=(1,0)$ supersymmetry in two dimensions, as the dimension and amount of supersymmetry are too small.}
Indeed, so long as a twisted supercharge $\cQ$ is nonzero, 
one finds that the image of the map $[\cQ,-] = \Gamma(\cQ,-)$ from \eqref{e:Gamma} is at least $n$-dimensional.
A {\em minimal} or {\em holomorphic} supercharge is one for which the dimension is exactly~$n$,
and we declare the image of $\cQ$ as spanned by the anti-holomorphic vector fields~$\{\del / \del \zbar_i\}$.

If a classical field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^\cQ$ of $\cT^\cQ$ has the form
\[
S^\cQ(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(\cQ \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $\cQ$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $\cQ$).
For a systematic discussion of how the twisted theory is defined, 
we refer to~\autocite{CostelloHolomorphic, ESW}.

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are BF theorires or Chern--Simons theories, possibly along with other fields in associated bundle; 
depending on the twist, that might mean a purely topological or purely holomorphic BF or Chern-Simons theory.
In even dimensions $d = 2n$, a minimal twist renders the theory holomorphic.
$\cQ$ itself determines the homotopies $\{\eta_i\}$ such that 
\beqn
[\cQ,\eta_i] = \frac{\del}{\del \zbar_i} ,
\eeqn 
recovering the characterization of holomorphic field theories mentioned at the beginning of the subsection.

As a representative example of twisting, 
consider four-dimensional space $\RR^4$ with $\cN=1$ supersymmetry.
The odd part of the supersymmetry algebra $\ft^1$ is four-dimensional, 
and every nonzero twist is minimal and gives us a copy of $\CC^2$.\footnote{And in a natural sense, they are all equivalent.}
That is, with this amount of supersymmetry, there does {\it not} exist a topological twist.
consider the fundamental example of pure four-dimensional supersymmetric Yang--Mills theory with $\cN=1$ supersymmetry. 
Its holomorphic twist is equivalent to holomorphic BF theory on~$\CC^2$ described in Section~\ref{sec: hol BF dfn}.

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, holomorphic BF theory on (super) twistor space associated to $\RR^4$ is equivalent to a self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \og{is there some other place to point?}

@@

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
